---
title: "SW RAVG FVS canopy cover adjustment"
author: "Alicia Reiner"
date: "6/16/2021"
output: 
  html_document: 
    keep_md: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The purpose of this code is to create adjust post-fire canopy cover, and canopy cover change with fire for scorch because FVS canopy cover does not account for crown cover loss due to scorch.

## Load Data and Packages

Load all of field data and subset out the 'oversampled' plots, 
those for which we have both field and Photo interp methods.  

```{r Southwest RAVG}
SWRAVG=read.csv("RAVG_V18.csv",header=TRUE, sep=",")

#subset out just the OS plots (rows,cols)
SWRAVG.OS<-SWRAVG[which(SWRAVG$OS=="Y"),]

#create difference between pdFVSVU and pdTreeCCloss
d_dFVSVU.dPI<-SWRAVG.OS$pdFVSVU-SWRAVG.OS$pdTreeCCloss
SWRAVG.OS<-cbind(SWRAVG.OS,d_dFVSVU.dPI)

library(FNN)
library(smatr)

plot(SWRAVG.OS$pdFVSVU,SWRAVG.OS$pdTreeCCloss)
plot(SWRAVG.OS$W_PctGrn_Tree,SWRAVG.OS$pdTreeCCloss)
plot(SWRAVG.OS$W_PctGrn_Tree,SWRAVG.OS$pdFVSVU)

```


### build KNN regression for prediction

next task is to create KNN regression from all tst and trn data (all OS plots)
and then create predictions for the difference in dcancov between methods using (overall) CBI


```{r SW RAVG build KNN}
#create x and y for knn reg:
x_RAVG.OS=SWRAVG.OS["W_PctGrn_Tree"]
y_RAVG.OS=SWRAVG.OS["d_dFVSVU.dPI"]

# need to import all field data .csv for 'xnew', the new data for which the knn will make predictions
SWRAVG.Field=read.csv("RAVG_V18_field.csv", header=TRUE, sep=",")

RAVG_pctG=SWRAVG.Field["W_PctGrn_Tree"]

#create a knn regression from just the OS plots and make predictions on the entire field dataset
pred_knn_All = FNN::knn.reg(train = x_RAVG.OS, test = RAVG_pctG, y=y_RAVG.OS, k=24)

#look at the values of adjustment
summary(pred_knn_All$pred)
plot(SWRAVG.Field$W_PctGrn_Tree,pred_knn_All$pred, xlab="Tree portion of CBI", ylab="KNN regression prediction")

### Create adjustment
adj2.pdFVSVU<-SWRAVG.Field$pdFVSVU-pred_knn_All$pred
SWRAVG.Field<-cbind(SWRAVG.Field, adj2.pdFVSVU)

#limit adjustment to 100% and only apply where W_PctGrn_Tree>0.5
adj.lim.pdFVSVU<-ifelse(SWRAVG.Field$adj2.pdFVSVU>1,1,ifelse(SWRAVG.Field$W_PctGrn_Tree<0.5,SWRAVG.Field$pdFVSVU,SWRAVG.Field$adj2.pdFVSVU))
#bind to dataframe
SWRAVG.Field<-cbind(SWRAVG.Field,adj.lim.pdFVSVU)

#resubset to create OS graphs
SWRAVG.OS.2<-SWRAVG.Field[which(SWRAVG.Field$OS=="Y"),]

plot(SWRAVG.OS.2$pdTreeCCloss,SWRAVG.OS.2$adj2.pdFVSVU)

plot(SWRAVG.OS.2$pdTreeCCloss,SWRAVG.OS.2$adj.lim.pdFVSVU, xlim=c(0,1), ylim=c(0,1), xlab="Photo interpretation canopy cover change", ylab="Adjusted FVS canopy cover change", abline(coef = c(0,1)))


```

### Slope Test

Now go back to just the OS plots and see if slope between pdTreeCCloss and adj.lim.pdFVSVU are 1, meaning that the data are essentially saying the same thing.


```{r SW RAVG slope test}

#slope test with pdFVSVU adjusted
with(SWRAVG.OS.2,slope.test(SWRAVG.OS.2$adj.lim.pdFVSVU, SWRAVG.OS.2$pdTreeCCloss, test.value=1, intercept=FALSE, method=0, alpha=0.1))

lm.fit.dif=lm(adj.lim.pdFVSVU~0+pdTreeCCloss,SWRAVG.OS.2)
summary(lm.fit.dif)

#write the adjustment to csv
write.csv(SWRAVG.Field,"RAVG_adjpdFVSVU_field.csv",sep = ",")

#added Nov 3, 2021: same plot as above, but with regression

plot(SWRAVG.OS.2$pdTreeCCloss,SWRAVG.OS.2$adj.lim.pdFVSVU, xlim=c(0,1), ylim=c(0,1), xlab="PI CC change", ylab="Scorch-adjusted FVS CC change", abline(lm.fit.dif))

```

