---
title: "SW RAVG final models July 2021"
author: "Alicia Reiner"
date: "19 Jan 2022"
output: 
  html_document: 
    keep_md: yes
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Load Data and Packages

first load field data

then load PI dataset

rescale CBI data so BEINF GAM distribution can be used (needs 0-1)

Note: revisions made to tidy up graphs 11/17/2021

```{r Southwest RAVG}
SWRAVG_field=read.csv("RAVG_V18_field.csv",header=TRUE, sep=",")
SWRAVG_PI=read.csv("RAVG_V18_PI.csv",header=TRUE, sep=",")
SWRAVG=read.csv("RAVG_V18.csv",header=TRUE, sep=",")

#create a combined field and PI canopy cover which uses an average if both are present.  
SWRAVG$pdCC<-ifelse(SWRAVG$OS=="Y",((SWRAVG$adj.lim.pdFVSVU+SWRAVG$pdTreeCCloss)/2),ifelse(is.na(SWRAVG$pdTreeCCloss)=="TRUE",SWRAVG$adj.lim.pdFVSVU,SWRAVG$pdTreeCCloss))
SWRAVG_field$pdCC<-ifelse(SWRAVG_field$OS=="Y",((SWRAVG_field$adj.lim.pdFVSVU+SWRAVG_field$pdTreeCCloss)/2),ifelse(is.na(SWRAVG_field$pdTreeCCloss)=="TRUE",SWRAVG_field$adj.lim.pdFVSVU,SWRAVG_field$pdTreeCCloss))

#remove outlier
SWRAVG_field<-SWRAVG_field[-which(SWRAVG_field$Plot=="BLUE11"),]
SWRAVG<-SWRAVG[-which(SWRAVG$Plot=="BLUE11"),]

CBI.B<-((1/3)*(SWRAVG_field$CBI-3)+1)
SWRAVG_field<-cbind(CBI.B,SWRAVG_field)

library(gamlss)
library(ggplot2) 
library(caret)
library(GenKern)
#had to install an older version of caret as package was not recognizing confMatrix()

#fix data types up front
SWRAVG_field$BPScode<-as.factor(SWRAVG_field$BPScode)
SWRAVG_PI$BPScode<-as.factor(SWRAVG_PI$BPScode)
SWRAVG$BPScode<-as.factor(SWRAVG$BPScode)


```



### CBI S_IA_dnbr_with

build model on whole dataset
test accuracy on whole dataset

```{r SW RAVG CBI gamlss S_IA_dnbr_with}

#rephrase results from stepGAICAll.A into the 'CBI.multivar' model below
CBI.simple<-gamlss(formula=CBI.B~S_IA_dnbr_with, sigma.formula=~S_IA_dnbr_with, nu.formula=~S_IA_dnbr_with, tau.formula=~S_IA_dnbr_with,family=BEINF,data=na.omit(SWRAVG_field))

CBI.simple

# extract new predictions for BEINF gamlss parameters for simple model
  CBI.simple.predAll <- predictAll(CBI.simple, newdata=SWRAVG_field, type="response") 
  mu.CBI.s <- CBI.simple.predAll$mu
  nu.CBI.s <- CBI.simple.predAll$nu
  tau.CBI.s <- CBI.simple.predAll$tau
  p0.CBI.s <- nu.CBI.s / (1+nu.CBI.s+tau.CBI.s) # probability of zeros
  p1.CBI.s <- tau.CBI.s / (1+nu.CBI.s+tau.CBI.s) # probability of ones

# calculate expected value for new predictions
yest.CBI.s.gamlss.IA <- (1-p0.CBI.s)*(p1.CBI.s+(1-p1.CBI.s)*mu.CBI.s)

#create confusion matrix for multivariate gamlss predictions

#first categorize the reserve CBI data (the CBI.B variable on 0-1 scale)
SWRAVG_field$CBI.cat=cut(SWRAVG_field$CBI.B,
                breaks=c(-Inf,0.0329,0.415,0.749,Inf),
                labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#then categorize the predicted data  
yest.CBI.s.cat=cut(yest.CBI.s.gamlss.IA,
                breaks=c(-Inf,0.0329,0.415,0.749,Inf),
                labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#Create Confusion Matrix
CBI.S.conf<-confusionMatrix(yest.CBI.s.cat, SWRAVG_field$CBI.cat,  dnn = c("Prediction", "Reference"))
print(CBI.S.conf)

CBI.testMSE<-mean((SWRAVG_field$CBI.B-yest.CBI.s.gamlss.IA)^2)
CBI.testMSE

plot(SWRAVG_field$S_IA_dnbr_with,yest.CBI.s.gamlss.IA, xlab="IA Sentinel-2 dNBR with offset", ylab="Predicted CBI")
plot(SWRAVG_field$CBI,yest.CBI.s.gamlss.IA, xlab="CBI", ylab="Predicted CBI")

```


###  BA gamlss S_IA_dnbr_with

BA simple gamlss run on whole dataset 

```{r SW RAVG BA gamlss S_IA_dnbr_with}


BA.simple<-gamlss(formula=pdBA~S_IA_dnbr_with, sigma.formula=~S_IA_dnbr_with,nu.formula=~S_IA_dnbr_with, tau.formula=~S_IA_dnbr_with,family=BEINF,data=na.omit(SWRAVG_field))

BA.simple

# extract new predictions for BEINF gamlss parameters for simple model
  BA.simple.predAll <- predictAll(BA.simple, newdata=SWRAVG_field, type="response") 
  mu.BA.s <- BA.simple.predAll$mu
  nu.BA.s <- BA.simple.predAll$nu
  tau.BA.s <- BA.simple.predAll$tau
  p0.BA.s <- nu.BA.s / (1+nu.BA.s+tau.BA.s) # probability of zeros
  p1.BA.s <- tau.BA.s / (1+nu.BA.s+tau.BA.s) # probability of ones

# calculate expected value for new predictions for simple model
yest.BA.s.gamlss.IA <- (1-p0.BA.s)*(p1.BA.s+(1-p1.BA.s)*mu.BA.s)

#first categorize the reserve pdBA data 
SWRAVG_field$pdBA.cat=cut(SWRAVG_field$pdBA,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#then categorize the predicted data  
yest.BA.s.cat=cut(yest.BA.s.gamlss.IA,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#Create Confusion Matrix
BA.S.conf<-confusionMatrix(yest.BA.s.cat, SWRAVG_field$pdBA.cat,  dnn = c("Prediction", "Reference"))
print(BA.S.conf)

BA.testMSE<-mean((SWRAVG_field$pdBA-yest.BA.s.gamlss.IA)^2)
BA.testMSE

plot(SWRAVG_field$S_IA_dnbr_with,yest.BA.s.gamlss.IA, xlab="IA Sentinel-2 dNBR with offset", ylab="Predicted percent BA change")
plot(SWRAVG_field$pdBA,yest.BA.s.gamlss.IA, xlab="Percent BA change", ylab="Predicted percent BA change")


```



### adj.lim.pdFVSVU gamlss S_IA_dnbr_with

on whole dataset

```{r SW RAVG adj.lim.pdFVSVU gamlss S_IA_dnbr_with}


adj.lim.pdFVSVU.simple<-gamlss(formula=adj.lim.pdFVSVU~S_IA_dnbr_with, sigma.formula=~S_IA_dnbr_with,nu.formula=~S_IA_dnbr_with, tau.formula=~S_IA_dnbr_with,family=BEINF,data=na.omit(SWRAVG_field))

adj.lim.pdFVSVU.simple

# extract new predictions for BEINF gamlss parameters for simple model
adj.lim.pdFVSVU.simple.predAll <- predictAll(adj.lim.pdFVSVU.simple, newdata=SWRAVG_field, type="response") 
  mu.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$mu
  nu.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$nu
  tau.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$tau
  p0.adj.lim.pdFVSVU.s <- nu.adj.lim.pdFVSVU.s / (1+nu.adj.lim.pdFVSVU.s+tau.adj.lim.pdFVSVU.s) # propdabbility of zeros
  p1.adj.lim.pdFVSVU.s <- tau.adj.lim.pdFVSVU.s / (1+nu.adj.lim.pdFVSVU.s+tau.adj.lim.pdFVSVU.s) # probability of ones

# calculate expected value for new predictions for simple model
yest.adj.lim.pdFVSVU.s.gamlss.IA <- (1-p0.adj.lim.pdFVSVU.s)*(p1.adj.lim.pdFVSVU.s+(1-p1.adj.lim.pdFVSVU.s)*mu.adj.lim.pdFVSVU.s)


#first categorize the reserve pdBA data 
SWRAVG_field$adj.lim.pdFVSVU.cat=cut(SWRAVG_field$adj.lim.pdFVSVU,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#then categorize the predicted data  
yest.adj.lim.pdFVSVU.s.cat=cut(yest.adj.lim.pdFVSVU.s.gamlss.IA,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#Create Confusion Matrix
adj.lim.pdFVSVU.S.conf<-confusionMatrix(yest.adj.lim.pdFVSVU.s.cat, SWRAVG_field$adj.lim.pdFVSVU.cat,  dnn = c("Prediction", "Reference"))
print(adj.lim.pdFVSVU.S.conf)

CC.testMSE<-mean((SWRAVG_field$adj.lim.pdFVSVU-yest.adj.lim.pdFVSVU.s.gamlss.IA)^2)
CC.testMSE

plot(SWRAVG_field$S_IA_dnbr_with,yest.adj.lim.pdFVSVU.s.gamlss.IA, xlab="IA Sentinel-2 dNBR with offset", ylab="Predicted percent CC change")
plot(SWRAVG_field$adj.lim.pdFVSVU,yest.adj.lim.pdFVSVU.s.gamlss.IA, xlab="Percent CC change", ylab="Predicted percent CC change")

```



### CBI S_EA_rbr_with

build model on whole dataset
test accuracy on whole dataset

```{r SW RAVG CBI gamlss S_EA_nbr_with}

#rephrase results from stepGAICAll.A into the 'CBI.multivar' model below
CBI.simple<-gamlss(formula=CBI.B~S_EA_rbr_with, sigma.formula=~S_EA_rbr_with, nu.formula=~S_EA_rbr_with, tau.formula=~S_EA_rbr_with,family=BEINF,data=na.omit(SWRAVG_field))

CBI.simple

# extract new predictions for BEINF gamlss parameters for simple model
  CBI.simple.predAll <- predictAll(CBI.simple, newdata=SWRAVG_field, type="response") 
  mu.CBI.s <- CBI.simple.predAll$mu
  nu.CBI.s <- CBI.simple.predAll$nu
  tau.CBI.s <- CBI.simple.predAll$tau
  p0.CBI.s <- nu.CBI.s / (1+nu.CBI.s+tau.CBI.s) # probability of zeros
  p1.CBI.s <- tau.CBI.s / (1+nu.CBI.s+tau.CBI.s) # probability of ones

# calculate expected value for new predictions
yest.CBI.s.gamlss <- (1-p0.CBI.s)*(p1.CBI.s+(1-p1.CBI.s)*mu.CBI.s)

#create confusion matrix for multivariate gamlss predictions

#first categorize the reserve CBI data (the CBI.B variable on 0-1 scale)
SWRAVG_field$CBI.cat=cut(SWRAVG_field$CBI.B,
                breaks=c(-Inf,0.0329,0.415,0.749,Inf),
                labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#then categorize the predicted data  
yest.CBI.s.cat=cut(yest.CBI.s.gamlss,
                breaks=c(-Inf,0.0329,0.415,0.749,Inf),
                labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#Create Confusion Matrix
CBI.S.conf<-confusionMatrix(yest.CBI.s.cat, SWRAVG_field$CBI.cat,  dnn = c("Prediction", "Reference"))
print(CBI.S.conf)

CBI2.testMSE<-mean((SWRAVG_field$CBI.B-yest.CBI.s.gamlss)^2)
CBI2.testMSE

plot(SWRAVG_field$S_EA_rbr_with,yest.CBI.s.gamlss, xlab="EA Sentinel-2 RBR with offset", ylab="Predicted CBI")
plot(SWRAVG_field$CBI,yest.CBI.s.gamlss, xlab="CBI", ylab="Predicted CBI")

```


###  BA gamlss S_EA_rbr_with

BA simple gamlss run on whole dataset 

```{r SW RAVG BA gamlss S_EA_rbr_with}


BA.simple<-gamlss(formula=pdBA~S_EA_rbr_with, sigma.formula=~S_EA_rbr_with,nu.formula=~S_EA_rbr_with, tau.formula=~S_EA_rbr_with,family=BEINF,data=na.omit(SWRAVG_field))

BA.simple

# extract new predictions for BEINF gamlss parameters for simple model
  BA.simple.predAll <- predictAll(BA.simple, newdata=SWRAVG_field, type="response") 
  mu.BA.s <- BA.simple.predAll$mu
  nu.BA.s <- BA.simple.predAll$nu
  tau.BA.s <- BA.simple.predAll$tau
  p0.BA.s <- nu.BA.s / (1+nu.BA.s+tau.BA.s) # probability of zeros
  p1.BA.s <- tau.BA.s / (1+nu.BA.s+tau.BA.s) # probability of ones

# calculate expected value for new predictions for simple model
yest.BA.s.gamlss <- (1-p0.BA.s)*(p1.BA.s+(1-p1.BA.s)*mu.BA.s)

#first categorize the reserve pdBA data 
SWRAVG_field$pdBA.cat=cut(SWRAVG_field$pdBA,
                 breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))
#then categorize the predicted data  
yest.BA.s.cat=cut(yest.BA.s.gamlss,
               breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#Create Confusion Matrix
BA.S.conf<-confusionMatrix(yest.BA.s.cat, SWRAVG_field$pdBA.cat,  dnn = c("Prediction", "Reference"))
print(BA.S.conf)

BA2.testMSE<-mean((SWRAVG_field$pdBA-yest.BA.s.gamlss)^2)
BA2.testMSE

plot(SWRAVG_field$S_EA_rbr_with,yest.BA.s.gamlss, xlab="EA Sentinel-2 RBR with offset", ylab="Predicted percent BA change")
plot(SWRAVG_field$pdBA,yest.BA.s.gamlss, xlab="Percent BA change", ylab="Predicted percent BA change")


```



### adj.lim.pdFVSVU gamlss S_EA_rbr_with

on whole dataset

```{r SW RAVG adj.lim.pdFVSVU gamlss S_EA_rbr_with}


adj.lim.pdFVSVU.simple<-gamlss(formula=adj.lim.pdFVSVU~S_EA_rbr_with, sigma.formula=~S_EA_rbr_with,nu.formula=~S_EA_rbr_with, tau.formula=~S_EA_rbr_with,family=BEINF,data=na.omit(SWRAVG_field))

adj.lim.pdFVSVU.simple

# extract new predictions for BEINF gamlss parameters for simple model
adj.lim.pdFVSVU.simple.predAll <- predictAll(adj.lim.pdFVSVU.simple, newdata=SWRAVG_field, type="response") 
  mu.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$mu
  nu.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$nu
  tau.adj.lim.pdFVSVU.s <- adj.lim.pdFVSVU.simple.predAll$tau
  p0.adj.lim.pdFVSVU.s <- nu.adj.lim.pdFVSVU.s / (1+nu.adj.lim.pdFVSVU.s+tau.adj.lim.pdFVSVU.s) # propdabbility of zeros
  p1.adj.lim.pdFVSVU.s <- tau.adj.lim.pdFVSVU.s / (1+nu.adj.lim.pdFVSVU.s+tau.adj.lim.pdFVSVU.s) # probability of ones

# calculate expected value for new predictions for simple model
yest.adj.lim.pdFVSVU.s.gamlss <- (1-p0.adj.lim.pdFVSVU.s)*(p1.adj.lim.pdFVSVU.s+(1-p1.adj.lim.pdFVSVU.s)*mu.adj.lim.pdFVSVU.s)

#first categorize the reserve pdBA data 
SWRAVG_field$adj.lim.pdFVSVU.cat=cut(SWRAVG_field$adj.lim.pdFVSVU,
                           breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#then categorize the predicted data  
yest.adj.lim.pdFVSVU.s.cat=cut(yest.adj.lim.pdFVSVU.s.gamlss,
                           breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#Create Confusion Matrix
adj.lim.pdFVSVU.S.conf<-confusionMatrix(yest.adj.lim.pdFVSVU.s.cat, SWRAVG_field$adj.lim.pdFVSVU.cat,  dnn = c("Prediction", "Reference"))
print(adj.lim.pdFVSVU.S.conf)

CC2.testMSE<-mean((SWRAVG_field$adj.lim.pdFVSVU-yest.adj.lim.pdFVSVU.s.gamlss)^2)
CC2.testMSE

plot(SWRAVG_field$S_EA_rbr_with,yest.adj.lim.pdFVSVU.s.gamlss, xlab="EA Sentinel-2 RBR with offset", ylab="Predicted percent CC change")
plot(SWRAVG_field$adj.lim.pdFVSVU,yest.adj.lim.pdFVSVU.s.gamlss, xlab="Percent CC change", ylab="Predicted percent CC change")

```



### CBI Confusion Matrices (Miller) EA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation 

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG CBI Confusion Matrix Miller EA}

CBI.pred.Miller<-ifelse(SWRAVG_field$L_EA_rdnbr_with<53, 0, ifelse(SWRAVG_field$L_EA_rdnbr_with>=986, 3, (1/0.389)*log((SWRAVG_field$L_EA_rdnbr_with+369)/421.7)))


#categorize Miller predictions

CBI.pred.Miller.cat=cut(CBI.pred.Miller,
                breaks=c(-Inf,0.99,1.249,2.249,Inf),
                      labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#use categorized predicted data and Miller predictions, both for whole set, in confusion matrix

#categorize the reserve CBI data
SWRAVG_field$CBI.cat=cut(SWRAVG_field$CBI.B,
                   breaks=c(-Inf,0.0329,0.415,0.749,Inf),
                labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))


#print("Confusion Matrix for Miller CBI model")
Miller.CBI.conf<-confusionMatrix(CBI.pred.Miller.cat, SWRAVG_field$CBI.cat, dnn = c("Prediction", "Reference"))

print(Miller.CBI.conf)

CBIMiller.testMSE<-mean((SWRAVG_field$CBI.B-CBI.pred.Miller)^2)
CBIMiller.testMSE

plot(SWRAVG_field$L_EA_rdnbr_with,CBI.pred.Miller, xlab="EA Landsat RdNBR with offset", ylab="Predicted CBI")
plot(SWRAVG_field$CBI,CBI.pred.Miller, xlab="CBI", ylab="Predicted CBI")


```



### BA Confusion Matrices (Miller) using equations from document for EA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation 

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG BA Confusion Matrix Miller EA}

  
BA.pred.Miller<-ifelse(SWRAVG_field$L_EA_rdnbr_with<167, 0, ifelse(SWRAVG_field$L_EA_rdnbr_with>=778, 1, (sin((SWRAVG_field$L_EA_rdnbr_with-166.5)/389))))

#then categorize the predicted data  
BA.pred.Miller.cat=cut(BA.pred.Miller,
                             breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#first categorize the reserve pdBA data 
SWRAVG_field$pdBA.cat=cut(SWRAVG_field$pdBA,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))
#use categorized predicted data and Miller predictions, both for whole data set, in confusion matrix

#print("Confusion Matrix for Miller BA model using equations from document")
Miller.BA.conf<-confusionMatrix(BA.pred.Miller.cat, SWRAVG_field$pdBA.cat,  dnn = c("Prediction", "Reference"))
print(Miller.BA.conf)

BAMiller.testMSE<-mean((SWRAVG_field$pdBA-BA.pred.Miller)^2)
BAMiller.testMSE

plot(SWRAVG_field$L_EA_rdnbr_with,BA.pred.Miller, xlab="EA Landsat RdNBR with offset", ylab="Predicted percent BA change")
plot(SWRAVG_field$pdBA,BA.pred.Miller, xlab="Percent BA change", ylab="Predicted percent BA change")

```



### CC loss Confusion Matrices (Miller) using equations from document for EA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG CCloss Confusion Matrix Miller for EA}


CC.pred.Miller<-ifelse(SWRAVG_field$L_EA_rdnbr_with<161, 0, ifelse(SWRAVG_field$L_EA_rdnbr_with>=778, 1, (sin((SWRAVG_field$L_EA_rdnbr_with-161)/392.6))))

#then categorize the predicted data  
CC.pred.Miller.cat=cut(CC.pred.Miller,
                          breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#use categorized predicted data and Miller predictions, both for whole set, in confusion matrix

#print("Confusion Matrix for Miller CC model using equations from document")
Miller.CC.conf<-confusionMatrix(CC.pred.Miller.cat, SWRAVG_field$adj.lim.pdFVSVU.cat,  dnn = c("Prediction", "Reference"))
print(Miller.CC.conf)

CCMiller.testMSE<-mean((SWRAVG_field$adj.lim.pdFVSVU-CC.pred.Miller)^2)
CCMiller.testMSE

plot(SWRAVG_field$L_EA_rdnbr_with,CC.pred.Miller, xlab="EA Landsat RdNBR with offset", ylab="Predicted percent CC change")
plot(SWRAVG_field$adj.lim.pdFVSVU,CC.pred.Miller, xlab="Percent CC change", ylab="Predicted percent CC change")


```




### CBI Confusion Matrices (Miller) IA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation 

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG CBI Confusion Matrix Miller IA}

CBI.pred.Miller.IA<-ifelse(SWRAVG_field$L_EA_rdnbr_with<60, 0, ifelse(SWRAVG_field$L_EA_rdnbr_with>=1127, 3, (1/0.389)*log(((SWRAVG_field$L_EA_rdnbr_with/1.1438)+369)/421.7)))


#categorize Miller predictions

CBI.pred.Miller.cat.IA=cut(CBI.pred.Miller.IA,
                breaks=c(-Inf,0.99,1.249,2.249,Inf),
               labels=c("0-<0.1","0.1-<1.25","1.25-<2.25","2.25-3"))

#use categorized predicted data and Miller predictions, both for whole set, in confusion matrix

#print("Confusion Matrix for Miller CBI model")
Miller.CBI.conf.IA<-confusionMatrix(CBI.pred.Miller.cat.IA, SWRAVG_field$CBI.cat, dnn = c("Prediction", "Reference"))

print(Miller.CBI.conf.IA)

CBIMillerIA.testMSE<-mean((SWRAVG_field$CBI.B-CBI.pred.Miller.IA)^2)
CBIMillerIA.testMSE

plot(SWRAVG_field$L_EA_rdnbr_with,CBI.pred.Miller.IA, xlab="IA Landsat RdNBR with offset", ylab="Predicted CBI")
plot(SWRAVG_field$CBI,CBI.pred.Miller.IA, xlab="CBI", ylab="Predicted CBI")


```



### BA Confusion Matrices (Miller) using equations from document for IA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation 

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG BA Confusion Matrix Miller IA}

  
BA.pred.Miller.IA<-ifelse(SWRAVG_field$L_EA_rdnbr_with<190, 0, ifelse(SWRAVG_field$L_EA_rdnbr_with>=889, 1, (sin((((SWRAVG_field$L_EA_rdnbr_with/1.1438)-166.5)/389))^2)))

#then categorize the predicted data  
BA.pred.Miller.cat.IA=cut(BA.pred.Miller.IA,
                             breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))
#first categorize the reserve pdBA data 
SWRAVG_field$pdBA.cat=cut(SWRAVG_field$pdBA,
                    breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))

#use categorized predicted data and Miller predictions, both for whole data set, in confusion matrix

#print("Confusion Matrix for Miller BA model using equations from document")
Miller.BA.conf.IA<-confusionMatrix(BA.pred.Miller.cat.IA, SWRAVG_field$pdBA.cat,  dnn = c("Prediction", "Reference"))
print(Miller.BA.conf.IA)

BAMillerIA.testMSE<-mean((SWRAVG_field$pdBA-BA.pred.Miller.IA)^2)
BAMillerIA.testMSE

plot(SWRAVG_field$L_EA_rdnbr_with,BA.pred.Miller.IA, xlab="IA Landsat RdNBR with offset", ylab="Predicted percent BA change")
plot(SWRAVG_field$pdBA,BA.pred.Miller.IA, xlab="Percent BA change", ylab="Predicted percent BA change")


```



### CC loss Confusion Matrices (Miller) using equations from document for IA

Now running a confusion Matrix where predictions are from the standard RAVG (Miller) equation

model run on RdNBR, the predictor for Miller equations

```{r SW RAVG CCloss Confusion Matrix Miller for IA}


CC.pred.Miller.IA<-ifelse(SWRAVG_field$L_IA_rdnbr_with<184, 0, ifelse(SWRAVG_field$L_IA_rdnbr_with>=890, 1, (sin((((SWRAVG_field$L_IA_rdnbr_with/1.1438)-161)/392.6))^2)))

#then categorize the predicted data  
CC.pred.Miller.cat.IA=cut(CC.pred.Miller,
                             breaks=c(-Inf,0.0999,0.24999,0.4999,0.74999,0.8999, Inf),
                labels=c("0-<10%","10-<25%","25-<50%","50-<75%","75-<90%","90-100%"))


#use categorized predicted data and Miller predictions, both for whole set, in confusion matrix

#print("Confusion Matrix for Miller CC model using equations from document")
Miller.CC.conf.IA<-confusionMatrix(CC.pred.Miller.cat.IA, SWRAVG_field$adj.lim.pdFVSVU.cat,  dnn = c("Prediction", "Reference"))
print(Miller.CC.conf.IA)

CCMillerIA.testMSE<-mean((SWRAVG_field$adj.lim.pdFVSVU-CC.pred.Miller.IA)^2)
CCMillerIA.testMSE

plot(SWRAVG_field$L_IA_rdnbr_with,CC.pred.Miller.IA, xlab="IA Landsat RdNBR with offset", ylab="Predicted percent CC change")
plot(SWRAVG_field$adj.lim.pdFVSVU,CC.pred.Miller.IA, xlab="Percent CC change", ylab="Predicted percent CC change")


```




